Palmer amaranth (*Amaranthus palmeri*) adaptation to agroecossystems

### 2021-07-29 Manuscript/Manuscript.Rmd
gfg

Monthly mean air temperature and sum precipitation were collected from June through September across the five locations in 2018 and 2019 (Figure 1)

>>>>

Monthly mean air temperature and sum precipitation were obtained using Daymet weather data from June through September across the five locations in 2018 and 2019 [@correndo2021] (Figure 1)
